\newcounter{row}
\newcommand\row{\stepcounter{row}\arabic{row}}
\chapter{INTRODUCTION}
\label{ch:introduction}%
% The \label{...}% enables to remove the small indentation that is generated, always leave the % symbol.

\section{Purpose}
Electric vehicles are the key technology to reduce the environmental impact of road transport, a sector that accounts for 16\% of global emissions. Recent years have seen exponential growth in the sale of electric vehicles together with improved range, wider model availability and increased performance. \\ \\
This trend is projected to continue in the future, and for this reason more charging stations are being built each year, in order to satisfy the increasing demand for energy for these electric vehicles. \\ \\
In this context, it is fundamental that the communication between the charging stations and the drivers is managed in such a way that it introduces minimal interference and constraints on 
our daily schedule. \\ \\
eMall is going to be a platform that permits the aforementioned communication through its subsystems eMSP (e-Mobility Service Provider), which is the app used by some users, like drivers, and the CPMS (Charge Point Management System), used by the owner of the charging stations or also called Charging Point Operator (CPO). \\ \\
Our main goal is to develop both subsystems and in particular, describe how the eMSPs can communicate with different CPMSs. Through an eMSP, drivers can easily choose where to charge their vehicles and easily book the charging process and pay for it. On the other hand, CPOs can use their CPMS to manage their charging stations, in order to improve and speed up the energy management and the charging process.
\label{sec:purpose}
\subsection{Goals} %AP
\label{subsec:goals}
\begin{table}[H]

\centering 
    \begin{tabular}{| p{0.15\linewidth} | p{0.85\linewidth} |}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{ID} & \textbf{Description} \T\B \\
    \hline \hline
    \textbf{G\row} & Allow Drivers to check nearby charging stations and see info about their prices, special offers and availability.\T\B\\
    \hline
    \textbf{G\row} & Allow Drivers to create and delete bookings for charging their vehicle in a charging station. \T\B\\
    \hline
    \textbf{G\row} & Allow Drivers to manage and monitor their charging process.\T\B\\
    \hline
    \textbf{G\row} & Allow Drivers to pay CPOs for the charging process provided.\T\B\\
    \hline
    \textbf{G\row} & Proactively suggest to the Drivers where to go to charge their vehicle.\T\B\\
    \hline
    \textbf{G\row} & Allow CPOs to manage the charging prices and the criteria of energy acquisition in their charging stations.\T\B\\
    \hline
    %\textbf{G\row} & Allow CPOs to dynamically decide how to acquire energy and how to distribute it in the charging station.\T\B\\
    %\hline
    \textbf{G\row} & Allow CPOs to connect to all their charging stations and monitor them.\T\B\\
    \hline
    \end{tabular}
    \\[10pt]
    \caption{Goals}
    \setcounter{row}{0}
\end{table}

\section{Scope}
\label{sec:scope}
The eMall platform objective is the integration between two subsystems: the eMSP and the CPMS. \\
Even though the eMSPs could be handled directly by third-party providers, in this project both subsystems are managed by eMall. \\ 
In this project, only the subsystems are described, since eMall is considered an already implemented service accessible via web and therefore only mentioned if the actors or the subsystems interact with it.
Among the several stakeholders to consider, this document concerns only drivers and CPOs. Occasionally DSOs (Distribution System Operators) are mentioned, but they should not be considered part of the project scope since they do not use the platform and are therefore external entities. \\


\subsection{World Phenomena} %AS
\label{subsec:worldPhenomena}
\begin{table}[H]
\centering 
    \begin{tabular}{| p{0.15\linewidth} | p{0.8\linewidth} |}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{ID} & \textbf{Description} \T\B \\
    \hline \hline
    \textbf{WP\row} & The driver wants to charge his vehicle.\T\B\\
    \hline
    \textbf{WP\row} & The driver drives the vehicle to the booked charging socket.\T\B\\
    \hline
    \textbf{WP\row} & The CPO wants to connect one of his charging stations.\T\B\\
    \hline
    \textbf{WP\row} & The CPO decides to start using a new eMSP.\T\B\\
    \hline
    \textbf{WP\row} & A DSO updates its energy price.\T\B\\
    \hline
    \end{tabular}
    \\[10pt]
    \caption{World Phenomena}
    \setcounter{row}{0}
\end{table}

\subsection{Shared Phenomena} %ES
\label{subsec:sharedPhenomena}
\begin{longtable}{| p{0.15\linewidth} | p{0.5\linewidth} |P{0.1\linewidth} | P{0.1\linewidth}|}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{ID} & \textbf{Description} & \textbf{W. C.} &\textbf{M. C.} \\
    \hline \hline
    
    \textbf{SP\row} & The Driver inserts his personal data and a payment method in order to register himself on the platform&\textbf{X} & \T\B\\
    \hline
    \textbf{SP\row}& The Driver creates a physical connection between the system and his vehicle. &\textbf{X} & \T\B\\
    \hline
    \textbf{SP\row} & The Driver receives a suggestion when he needs to charge the vehicle. & & \textbf{X}\T\B\\
    \hline
    \textbf{SP\row} & The energy level of the battery vehicle changes. & \textbf{X} & \T\B\\
    \hline
    \textbf{SP\row} & The Driver follows a new navigation route on his vehicle. & \textbf{X} & \T\B\\
    \hline
    
    %\textbf{SP\row} & The CPO check the DSOs energy prices
    %&  \textbf{X}  & \\
    %\hline
    \textbf{SP\row} & The Driver checks information about the availability and locations of nearby charging stations 
    & \textbf{X} &\\
    \hline
    \textbf{SP\row} & The Driver books a charge in a charging station.  & \textbf{X} &\T\B\\
    \hline
    \textbf{SP\row} & The Driver receives a notification that the booking process was successful & &\textbf{X}  \T\B\\
    \hline
    \textbf{SP\row} & The Driver receives a notification that the booking was successfully cancelled & &\textbf{X}  \T\B\\
    \hline
    \textbf{SP\row} & The Driver plugs his vehicle in the charging socket  &\textbf{X}& \T\B\\
    \hline
    \textbf{SP\row} & The Driver gets notified when trying to start a charging process even though his vehicle is not well-connected & &\textbf{X} \T\B\\
    \hline
    \textbf{SP\row} & The Driver receives a notification when the charging process is complete. & & \textbf{X}\T\B\\
    \hline
    \textbf{SP\row} & The CPO checks the internal status of one of the managed charging stations 
    & \textbf{X} & \\
    \hline
    \textbf{SP\row} & The CPO sets a special offer. & \textbf{X} &\T\B\\
    \hline
    \textbf{SP\row} & The CPO changes energy acquisition criteria for a charging station 
    & \textbf{X} & \\
    \hline
    \textbf{SP\row} & The CPO changes energy revenue criteria for a charging station 
    & \textbf{X} & \\
    \hline
    \textbf{SP\row} & In a charging station a socket becomes available after a charging process is finished &  \textbf{X}& \T\B\\
    \hline
    \caption{Shared Phenomena}
    \setcounter{row}{0}
\end{longtable}
\newpage
\section{Definitions, Acronyms, Abbreviations}
\label{sec:definitionsAcronymsAbbreviations}
\subsection{Definitions} %AP
\label{subsec:definitions}
\begin{table}[H]
\centering 
    \begin{tabular}{| p{0.125\linewidth} | p{0.80\linewidth} |}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{Definition} & \textbf{Description} \T\B \\
    \hline \hline
    \textbf{Energy Provider} & The entity providing energy to the charging station, it can either be a DSO or the internal batteries of that charging station.\T\B\\
    \hline
    \textbf{Driver} & The person that will use the eMSP application. For shortening reasons, only male pronouns are used to address the driver. \T\B\\
    \hline
    \textbf{Charging Point Operator} & The legal owner of charging stations that will use the CPMS. For shortening reasons, only male pronouns are used to address the driver. \T\B\\
    \hline
    \textbf{Charging Station} & Physical place managed by a CPO where drivers can charge their vehicle. It has one or more charging sockets. When a charging station is "available, " one of its sockets is available. \T\B\\
    \hline
    \textbf{Charging Socket} & Plug where drivers connect their vehicle to charge it. It can support different charging types. When a charging socket is "available" it means that it has no booked charging process  or no one is connected to it.\T\B\\
    \hline
    \textbf{Maximum Amount Of Time} & The maximum amount of time a Driver can book a charge before the arrival time. It is needed to avoid a charging socket being occupied for a long time without being used. This variable can be decided when implementing the system \T\B\\
    \hline
    \textbf{Charging Type} & It defines the speed of the charging process.\T\B\\
    \hline
    \textbf{User} & Either the CPO or the Driver.\T\B\\
    \hline
    
    \end{tabular}
    \\[10pt]
    \caption{Definitions}
\end{table}

\subsection{Acronyms} %AS
\label{subsec:acronyms}
\begin{table}[H]
\centering 
    \begin{tabular}{| p{0.175\linewidth} | p{0.6\linewidth} |}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{Acronyms} & \textbf{Description} \T\B \\
    \hline \hline
    \textbf{eMall} & e-Mobility for All\T\B\\
    \hline
    \textbf{eMSP} & e-Mobility Service Provider\T\B\\
    \hline
    \textbf{CPO} & Charging Point Operator\T\B\\
    \hline
    \textbf{CPMS} & Charge Point Management System\T\B\\
    \hline
    \textbf{DSO} & Distribution System Operator\T\B\\
    \hline
    \textbf{FRE} & Functional REquirement\T\B\\
    \hline    
    \textbf{NFRE} & Non-Functional REquirement\T\B\\
    \hline
    \textbf{RASD} & Requirements Analysis and Specification Document\T\B\\
    \hline
    \textbf{W.C.} &  World Controlled\T\B\\
    \hline
    \textbf{M.C.} &  Machine Controlled\T\B\\
    \hline
    \textbf{ID} & IDentifier\T\B\\
    \hline
    \textbf{API} & Application Programming Interface\T\B\\
    \hline
    \end{tabular}
    \\[10pt]
    \caption{Acronyms}
\end{table}
\subsection{Abbreviations} %AS
\label{subsec:abbreviations}
\begin{table}[H]
\centering 
    \begin{tabular}{| p{0.2\linewidth} | p{0.4\linewidth} |}
    \hline
    \rowcolor{bluepoli!40}
     \textbf{Abbreviation} & \textbf{Description} \T\B \\
    \hline \hline
    \textbf{Gx} & Goal number $X$\T\B\\
    \hline
    \textbf{WPx} &  World Phenomenon number $X$\T\B\\
    \hline
    \textbf{SPx} &  Shared Phenomenon number $X$\T\B\\
    \hline
    \textbf{Dx} & Domain Assumption number $X$ \T\B\\
    \hline
    \textbf{FREx} & Functional Requirement number $X$ \T\B\\
    \hline
    \textbf{NFREx} & Non-Functional Requirement number $X$ \T\B\\
    \hline
    \textbf{Ux} & Use Case number $X$ \T\B\\
    \hline
    \textbf{opt} & Optional \T\B\\
    \hline
    \textbf{alt} & Alternative  \T\B\\
    \hline   
    \end{tabular}
    \\[10pt]
    \caption{Abbreviations}
\end{table}
\label{sec:revisionHistory}
\section{Revision History}
\begin{table}[H]
\centering 
    \begin{tabular}{| P{0.2\linewidth} | p{0.15\linewidth} | p{0.55\linewidth}|}
        \hline
         \rowcolor{bluepoli!40}Version Number & Date & Description \T\B  \\
         \hline
         1.0& 22/12/2022 & First completed version of the documents.\T\B\\\hline
         1.1& 23/12/2022 & Rephrased and fixed minor bad wordings about bookings.\T\B\\\hline
         1.2& 01/01/2023 & Small fixes in sequence diagrams.\newline Added Calendar API.\T\B\\\hline
    \end{tabular}
    \caption{Versions history}
    \label{tab:my_label}
\end{table}
\section{Reference Documents} %AS
\label{sec:referenceDocuments}
\begin{itemize}
\item  The specification document “Assignment RDD AY 2022-2023\_v3.pdf”
\end{itemize}


\section{Document Structure}
\label{sec:documentStructure}
\paragraph{Section 1}
Introduction about the purpose and scope of the system. Discuss the main world and shared phenomena concerning our application’s domain and goals. Furthermore, we sum up all the definitions and abbreviations in order to have a better comprehension of the following chapters.
\paragraph{Section 2}
Introduction of different scenarios about the multiple interactions that the application could face. After that, there is a structural description of the system represented by various graphs such as class diagrams and state charts with all of their main characteristics. In the product functions section, there are multiple descriptions of all the possible functionalities present inside the application. In the last part, there is a list of the domain assumptions and the
characteristics of the users who will exploit the application.
\paragraph{Section 3}
This is the main part of the document, at the beginning, there is a description of the software and communication interfaces. After this, it’s shown all the use case diagrams of the systems and the corresponding use cases, followed by the respective sequence diagram. Then, 
the lists of the requirements are presented along with their description, and some tables that map goals and domain assumptions with the respective requirements.  In the end, there is a list of the performance requirements and design constraints of the system.
\paragraph{Section 4}
This section contains a formal description of the important parts of the system using
the Alloy language. 
\paragraph{Section 5}
This section shows how much time every student spent working on the documents
\paragraph{Section 6}
This section is made to point out all the references and tools used during the
creation of this document.